Computer vision entails mining information from images and video to extract meaningful information. We encounter state-of-the-art computer vision techniques every day-surveillance camera systems \cite{traffic_surveillance_pergamon} \cite{distributed_surveillance} \cite{vehicle_detection}, face detection in our digital cameras, sports analysis, and the recent very popular Kinect system by Microsoft \cite{Kinect_intro}, to name a few. In all of these situations, computer algorithms process images and video to get useful information, so that a human user need not look through, say, hours and hours of surveillance footage. Computer vision research has come a long way over the decades, and today you can take a picture of an object on your cellphone camera and search for it, without typing a word. \\

Particularly, we are focused on improving the computer vision algorithm together with a position estimator for surveillance operations. Task distribution \cite{Coop_Surv_aerial_JJ} \cite{Consensus_reaching_Xiao} \cite{Adaptative_tast_Meuth} \cite{distributed_architecture_Ivan_Maza}  is a key issue in surveillance, many approaches were based on reducing the size and the requirements of the UAVs but increasing the number of these ones. That allows to the system to simplify the tasks and reduce the areas of every vehicle. The Decentralized of the task \cite{descentralized_task_UAV} (That has the associated increasing of the number of the watchers) results in the need of a network that allows to every device to communicate each other and share their information. \\

In regard to the vision algorithm, there are many different method to extract information from every frame. These can be focused in shape segmentation and recognition \cite{shape_using_shape_context} \cite{Vehicle_recog_markov}, color segmentation \cite{} among others, including a combination of them \cite{realtime_signal_recon_shape_color} \cite{signal_recogn_shape_color} \cite{Robust_RT_tracking_color_face_Darrell}.


% 666 TODO....